Near and Mid-infrared properties of known $z\geq5$ Quasars

### 2019-06-12 tex/VHzQ.tex
Minor corrections to Section 4 text

Using the extended datasets described in Section~\ref{sec:NIR_data},
we select objects with at least 8 measurements observed with intervals
of at least 30 days, in at least one filter. The the average
calibrated flux over all epochs must be $>0$ (i.e. {\tt aperJky3}$>0$)
with the signal-to-noise is required to be $\geq8$. (i.e. {\tt
aperJky3/aperJky3Err}$\geq$8). The clipped median and standard
deviation is then calculated
\begin{equation}
      var = 1.48 \times  {\rm m.a.d.} / \bar{\epsilon}
\end{equation}
where $var$ is the index of variation, m.a.d. is the median absolute
deivation, and $\bar{\epsilon}$ is the mean of the error in each point
in the light curve, divided by the total number of points.  With these
criteria, there are 21 WFCAM and 12 VISTA objects with 1 object (VIK
J1148+0056) in common to both, and this sample of 32 is our starting
point for variability investigations.

@@

We finally focus on SDSS J0959+0227 which is presented in
\citet{WangF2016} but is first reported in \citet{Civano2011} as
CID-2220 and a high-redshift, $z>3$ AGN, in the Chandra-COSMOS
field. The spectrum from this object is presented in \citet{Ikeda2012}
and shows SDSS J0959+0227 having a narrow Ly$\alpha$ line, and would
likely be a Lyman-$\alpha$ emitting galaxy had it not been an X-ray
source, The X-ray luminosity is $\approx3x10^44$ erg s$-1$ in the 2–10
keV rest-frame, so it is an AGN. This object is clearly not a regular
broadline ``Type 1'' AGN. Noting that the redshift of $z=5.07$ for
SDSS J0959+0227, the $Y$, $J$, $H$, $Ks/K$-bands correspond to
rest-wavelengths of $\sim$1690, 2055, 2690, 3515/3625\AA\ i.e. the
rest-frame UV/very blue, so, so the regular blue QSO continuum could
be emerging Thus, with the slightest hint of variability, this could
potentially be a high-$z$ AGN transitioning from a narrow-line ``Type
2'' object to a broadline Type 1 quasar.

>>>>

Using the extended datasets described in Section~\ref{sec:NIR_data},
we select objects with at least 8 measurements observed with intervals
of at least 30 days, in at least one filter. The the average
calibrated flux over all epochs must be $>0$ (i.e. {\tt aperJky3}$>0$)
with the signal-to-noise is required to be $\geq8$. (i.e. {\tt
aperJky3/aperJky3Err}$\geq$8). The clipped median and median absolute
deviation is then calculated
\begin{equation}
      var = 1.48 \times  {\rm m.a.d.} / \bar{\epsilon}
\end{equation}
where $var$ is the index of variation, m.a.d. is the median absolute
deivation, and $\bar{\epsilon}$ is the mean of the error in each point
in the light curve, divided by the total number of points.  With these
criteria, there are 21 WFCAM and 12 VISTA objects with 1 object (VIK
J1148+0056) in common to both, and this sample of 32 is our starting
point for variability investigations.

@@

We finally focus on SDSS J0959+0227 which is presented in
\citet{WangF2016} but is first reported in \citet{Civano2011} as
CID-2220 and a high-redshift, $z>3$ AGN, in the Chandra-COSMOS
field. The spectrum from this object is presented in \citet{Ikeda2012}
and shows SDSS J0959+0227 having a narrow Ly$\alpha$ line, and would
likely be a Lyman-$\alpha$ emitting galaxy had it not been an X-ray
source, The X-ray luminosity is $\approx3\times10^44$ erg s$-1$ in the 2–10
keV rest-frame, so it is an AGN. This object is clearly not a regular
broadline ``Type 1'' AGN. Noting that the redshift of $z=5.07$ for
SDSS J0959+0227, the $Y$, $J$, $H$, $Ks/K$-bands correspond to
rest-wavelengths of $\sim$1690, 2055, 2690, 3515/3625\AA\ i.e. the
rest-frame UV/very blue, so, so the regular blue QSO continuum could
be emerging Thus, with the slightest hint of variability, this could
potentially be a high-$z$ AGN transitioning from a narrow-line ``Type
2'' object to a broadline Type 1 quasar.
